From Nested Virtualization Architecture \\To 2D Security Management for Distributed Clouds

### 2014-03-29 paper/draft.tex
Upd arch. comparison.

However, there is no TCB reduction as the code size running in L0 kernel space is as big as before. 
Besides, adopting a MH as L1 prevents using inter-platform enhanced features. As already seen for MH design, the price of having a thin hypervisor is normally paid with a lack of certain features. For example, XMHF only supports a single guest~\cite{xmhf}. Thus, this architectural approach cannot provide any new horizontal features leveraging NV. Therefore, this approach can only provide the same features as those deployed today, with an increased but not insufficient level of isolation.

@@

\noindent In this configuration, the TCB is smaller than for other architectures, due to the modular structure of micro-kernels., executed at L0. Leveraging as L1 a GPH, like Xen or KVM, provides to the user an environment apparently  identical to the one used in production today, satisfying DP5. The L1 GPH is normally integrated with modern cloud toolkits like OpenStack and will support 3rd part applications.
Therefore, the architecture presents a stronger isolation leveraging on nested virtualization, providing in particular a strong tiny core(DP3). The MH layer will be transparent from the user and it will not not any change in the functioning of the platform.

>>>>

However, there is no TCB reduction as the code size running in L0 kernel space is as big as before. 
Besides, adopting a MH as L1 prevents using inter-platform enhanced features. As already seen for MH design, the price of having a thin hypervisor is normally paid with a lack of certain features. For example, XMHF only supports a single guest~\cite{xmhf}. Thus, this architectural approach cannot provide any new horizontal features leveraging NV. Therefore, this approach can only provide the same features as those deployed today, with an increased but not sufficient level of isolation.

@@

\noindent This approach achieves a smaller TCB than other architectures, due increased modularity brought by the micro-kernel-like design of the L0 layer -- satisfying DP3. Leveraging a GPH like Xen or KVM for the L1 layer provides the user with an environment looking identical to those used in production today -- satisfying DP5. The L1 GPH is normally integrated with modern cloud toolkits like OpenStack and will thus support third-party applications -- satisfying DP4.
Therefore, this architecture achieves a stronger level of isolation due to vertical use of NV to introduce an additional hardware-protected security monitor. Thanks to the GPH, the MH layer remains transparent to the user and should not impact the functional properties of the IaaS platform.
